R Notebook

### 2024-10-05 Code/R/Research/Tensor MSSA.rmd
hosvd/tucker modification for complex numbers

tens3 <- function(s, I, L) {
  require("rTensor")
  v <- as.vector(s)
  N <- length(v)
  J <- N - I - L + 2
  X <- array(NA, c(I, L, J))
  for (i in 1:J) {
    X[, , i] <- outer(1:I, 1:L, function(x, y) s[i + x + y - 2])
  }
  return(as.tensor(X))
}

reconstruct.group3 <- function(X.tens) {
  X <- X.tens@data
  I <- length(X[, 1, 1])
  L <- length(X[1, , 1])
  J <- length(X[1, 1,])
  s <- vector(mode = "numeric", length = I + L + J - 2)
  for (C in 3:(I + L + J)) {
    sum <- 0
    count <- 0
    for (i in 1:(C - 2)) {
      for (l in 1:(C - 1 - i)) {
        if (i <= I && l <= L && C - i - l <= J) {
          sum <- sum + X[i, l, C - i - l]
          count <- count + 1
        }
      }
    }
    s[C - 2] <- sum / count
  }
  return(s)
}

>>>>

tens3 <- function(s, I, L) {
  require("rTensor")
  v <- as.vector(s)
  N <- length(v)
  J <- N - I - L + 2
  X <- outer(1:L, 1:J, function(l, j) l + j) |> outer(1:I, function(lj, i) s[lj + i - 2])
  return(as.tensor(X))
}

reconstruct.group3 <- function(X.tens) {
  stopifnot(is(X.tens, "Tensor"))
  X <- X.tens@data
  I <- length(X[, 1, 1])
  L <- length(X[1, , 1])
  J <- length(X[1, 1,])
  s <- vector(mode = "numeric", length = I + L + J - 2)
  for (C in 3:(I + L + J)) {
    sum <- 0
    count <- 0
    for (i in 1:(C - 2)) {
      for (l in 1:(C - 1 - i)) {
        if (i <= I && l <= L && C - i - l <= J) {
          sum <- sum + X[i, l, C - i - l]
          count <- count + 1
        }
      }
    }
    s[C - 2] <- sum / count
  }
  return(s)
}
